\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/BadUSBC.tex
Minor: abs

\begin{abstract}
The security of USB protocol has been paid extensive attention to, despite its wide usage.
Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
However, BadUSB suffers from several limitations.
Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
To our best knowledge, \tool is the first attack model utilizing USB Type-C.
To validate the usability and effectiveness, we conducted extensive experiments and a user study, in which 
\fengwei{What results?}we got valuable results.
\fengwei{what countermeasures do we propose? including isolated UI rendering.}
We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defense methods.
\end{abstract}

>>>>

\begin{abstract}
The security of USB protocol has been paid extensive attention to, despite its wide usage.
Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
However, BadUSB suffers from several limitations.
Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
To our best knowledge, \tool is the first attack model utilizing USB Type-C.
To validate the usability and effectiveness, we conducted extensive experiments and a user study, in which 
\fengwei{What results?}we got valuable results.
%\fengwei{what countermeasures do we propose? including isolated UI rendering.}
We also proposed reasonable countermeasures for our attack model, including isolated UI rendering, external hardware authorization and distrust-by-default, which may be inspiring for future research on defense methods.
\end{abstract}
